\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 prelims.tex
lazy fix

For a given $\tau$, we call the affine relation $f_\tau$ its update
relation, and the predicates $g_\tau$ and $g'_\tau$ as pre- and
post-conditions on the transition. The machine starts its operation in
location $\pLocI$ with an initial valuation $\nu_0$ to the variable
$\vx$ such that $\nu_0(\vx)$ satisfies $\Theta$.

@@

\begin{itemize}[noitemsep, leftmargin= 1.5 em]
\item
each transition of $A$ represents a discrete time step $\Delta$ of the
system $\System$,
\item
if the state-space of $\System$ is $\reals^n$, the the valuation
function for variable $\x$ in $A$ assigns $\x$ some value in
$\reals^n$,
\item
for the $N$ tuples $(v,v')$ discovered by simulation, if $v' = Av
+ B + \vec{\delta}$ represents the affine relation discovered using
linear regression, and if $h$ is the convex hull of all the $v$
states across all tuples and $h'$ is the convex hull of all the $v'$
states across all tuples, then $f_\tau \subseteq
\setof{(\nu(\x),\nu'(\x)) \mid \nu'(\x) \in A\x + B + \vec{\delta}}$,
and $g$ states that $\nu(\x)$ is in $h$, and $g'$ states that
$\nu'(\x) \in h'$.
\end{itemize}

@@

>>>>

For a given $\tau$, we call the affine relation $f_\tau$ its update
relation, and the predicates $g_\tau$ and $g'_\tau$ as pre- and
post-conditions on the transition. The machine starts its operation in
location $\pLocI$ with an initial valuation $\nu_0$ to the variable
$\vx$ such that $\nu_0(\vx)$ satisfies $\Theta$. For convenience, we
abuse notation, and use the name a variable as a proxy for a certain
valuation, and use the primed version of the variable as a proxy for
its valuation after a transition, \ie, $\vx$ is used instead of
$\nu(\vx)$ and $\vx'$ is used instead of $\nu'(\vx)$.

@@

\begin{itemize}[noitemsep, leftmargin= 1.5 em]
\item
each transition of $A$ represents a discrete time step $\Delta$ of the
system $\System$,
\item
if the state-space of $\System$ is $\reals^n$, the the valuation
function for variable $\x$ in $A$ assigns $\x$ some value in
$\reals^n$,
\item
for the $N$ tuples $(v,v')$ discovered by simulation, if $v' = Av
+ B + \vec{\delta}$ represents the affine relation discovered using
linear regression, and if $h$ is the convex hull of all the $v$
states across all tuples and $h'$ is the convex hull of all the $v'$
states across all tuples, then $f_\tau \subseteq
\setof{(\x,\x') \mid \x' \in A\x + B + \vec{\delta}}$,
and $g$ states that $\x$ is in $h$, and $g'$ states that
$\x' \in h'$.
\end{itemize}

@@

In what follows, we use the terms PWA relational model and PWA
transition system interchangeably to mean PWA relational model.
